Paper Report

### 2017-11-27 Paper_report.tex
Hierarchical multiscale recurrent neural networks

>>>>

%----------------------------------------------------------------------------------------
%	Hierarchical Multiscale Recurrent Neural Networks
%----------------------------------------------------------------------------------------

\section{Hierarchical Multiscale Recurrent Neural Networks}

\subsection{Main idea}
Hierarchical Multiscale RNNs learns the latent hierarchical structure of a sequence and its temporal representation with non-fixed timescales (Without explicit boundary information).

For example, this model consider a sentence as a list of characters, not only words. It is trained to know autonomously the beginning and the end of a word. For each layer, it could group the units.

The key idea is an update mechanism with a binary boundary detector (Gate determining the boundary of an object).\\

The advantages of "Multiscale" over standard RNNs:
\begin{itemize}
\item Updating the high-level layers is less frequently $\rightarrow$ Computational efficiency and Vanishing gradient problem. Solving vanishing gradient problem means that this model could delivering efficiently long-term dependencies.
\item Flexible resource allocation. The model could modify the number of hidden units for an information. For example, the model could use more units to the higher layers (Long-term dependency) and less units to the lower layers (Short-term dependency). This means that it could decide to keep the long-term or short-term information.

\item A good generalization performance (Dropout approach)
\item The internal process of RNN becomes more interpretable. We could count the number of operation execution time ( Update, Flush and Copy operation)
\end{itemize}

The problem of the previous kind of RNNs:
\begin{itemize}
\item LSTMs: LSTMs has also an update mechanism with forget and update gates, which means that it could operate with different timescales. However, these timescales are not organized hierarchically. \\
Problem:
	\begin{itemize}
	 \item In practice, after a few hundred time steps, long-term information is gradually diluted at every time step.
	 \item LSTMs is computationally expensive (Update at every time step for each unit)
 	\end{itemize}

\item Clockwork RNNs and its soft timescale approach: The hidden units are grouped into several modules. Different timescales are assigned to these modules (i.e: A module $i$ is updated at every $2^{i - 1}$ -th time step).\\
Problem:
	\begin{itemize}
	\item It is not easy to find a good timescales because timescale depends on data.
	\item It is unclear how to deploy more layers than the number of boundary levels that is explicitly observed in the data.
	\end{itemize}

\item Hierarchical RNNs with Known explicit hierarchical boundary structure (Not multiscale).\\ Problem: It is the same with Clockwork RNNs that boundary information is not explicit and expensive to be discovered.

\item CNNs with 1-D kernels: It could provide also high-level representation of sequence.\\
Problem: We need to observe a full sequence with a reduced length.

\item Zoneout, a regularization technique similar to dropout.\\
Problem: Its strength is still an hyper-parameter.

\end{itemize}

\subsection{Update mechanism}
They describe Hierarchical Multiscale RNN (HM-RNN) based on LSTM update rule. It is better to see the graph in paper.\\
\marginpar{Why it is not based on RNN ?}

At each time step $t$, for each layer $l$, there are:
\begin{equation}
h_t^l,\, c_t^l,\, z_t^l = f^l (c_{t-1}^l, h_{t-1}^l, h_t^{l-1}, h_{t-1}^{l+1}, z_{t-1}^l, z_t^{l-1})
\end{equation}

The function includes Update, Copy and Flush operation depending on binary detector - boundary states $z_{t-1}^l$ (Previous time step) and $z_t^{l-1}$ (Below layer).
The difference between three operations are the use of context $c$ which keeps the summary information of the previous units.
\begin{itemize}
\item \textbf{Flush}: It shows the beginning of a segment or "word", the boundary is found previously.
\\ The unit $h_t^l$ does not get information from same-level context $c_{t-1}^l$ (Eject) but higher-level unit $h_{t-1}^{l+1}$ (This is the connection between two words, it is re-installed with more long-term information from previous words).

\item  \textbf{Copy}: It shows not-end state of a "word", none of boundary is found.
\\ the unit  $h_t^l$ only copies from previous unit $h_{t-1}^l$, its context copies from $c_{t-1}^l$ (It reduces the number of operation execution, leading to computational efficiency).

\item \textbf{Update}: It is similar to update operation of LSTM (Forget, input and output gate) but it is executed sparsely. It is the end of a "word", the boundary is found in the unit below.
\\ The unit $h_t^l$ gets also information from the same-level context $c_{t-1}^l$ and information from the lower-level unit $h_t^{l-1}$, but not from the higher-level unit $h_{t-1}^{l+1}$ (It does not need information from previous words).
\end{itemize}

\subsection{Analysis}
The result for character-level language model does not show clearly a good performance.
